---
title: "Homework 4"
author: "Sidney Gerst"
date: "3/4/2020"
output:
  word_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

### 1. Climate Change 

```{r include = F}

climate_change <- read_csv("climate_change.csv")


```


**Geographic Range**

```{r echo = F, size=10}

geographic <- ggplot(climate_change, aes(x = Species, y = density_change, fill = geographic_range))+
  geom_bar(stat = "identity")+
  facet_wrap(~geographic_range, scales = "free_x") +
  theme_bw()+
  labs(title = "Geographic Range and the Change in Density from 1955",
       y = "Change in Density") +
  theme(legend.position = "none")

geographic



```

There is a pattern for each of the different geographic ranges. The Cosmopolitan species are split between positive and negative density change. The Northern species all had a negative change in density from the year 1955. The Southern species all had a positive change in density from the year 1955. This shows that climate change has a positive effect on Southern species and a negative effect on Northern species. 


larval stage

```{r size = 15}

larval <- ggplot(climate_change, aes(x = Species, y = density_change, fill = trophic_level))+
  geom_bar(stat = "identity")+
  facet_wrap(~geographic_range, scales = "free_x") +
  theme_bw()+
  labs(title = "Geographic Range and the Change in Density from 1955",
       y = "Change in Density") 
  #theme(legend.position = "none")

larval

development_change


```



**Trophic Level**

```{r echo=F}

trophic <- ggplot(climate_change, aes(x = Species, y = density_change, fill = trophic_level))+
  geom_bar(stat = "identity")+
  facet_wrap(~trophic_level, scales = "free_x") +
  theme_bw()+
  labs(title = "Trophic Level and the Change in Density from 1955",
       y = "Change in Density") +
  theme(legend.position = "none")

trophic



```

Scavengers had the most positive effect from climate change where five out of six species showed a positive change in density. 


### 2. Nuclear Power

```{r include = F}

nuclear <- read_csv("nuclearpowerplant.csv")

nuclearspecies <- read_csv("nuclear_species.csv")


```


**Species A**

```{r echo=F}

speciesa <- ggplot(nuclearspecies, aes(x = Year, y = A, fill = Plant)) +
  geom_bar(stat = "identity") +
  facet_wrap(~Plant) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 38)) +
  labs(title = "Density of Species A",
       y = "Number of Individuals per 100m^2 ")
  

speciesa

```

 

**Species B**

```{r echo=F}

speciesb <- ggplot(nuclearspecies, aes(x = Year, y = B, fill = Plant)) +
  geom_bar(stat = "identity") +
  facet_wrap(~Plant) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 40)) +
  labs(title = "Density of Species B",
       y = "Number of Individuals per 100m^2 ")
  

speciesb


```



**Species C**

```{r echo=F}

speciesc <- ggplot(nuclearspecies, aes(x = Year, y = C, fill = Plant)) +
  geom_bar(stat = "identity") +
  facet_wrap(~Plant) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 40)) +
  labs(title = "Density of Species C",
       y = "Number of Individuals per 100m^2 ")
  

speciesc



```

Hyperion Bay should be used as the control because it tracks closely to Diablo before the plant became operational. There doesn't seem to be any detectable impacts on species A from any of the areas sampled. There were detecable impacts on species B with a distinct drop at Diablo and Hyperion and a steady decline with a few peaks at Noway Bay. For species C there seemed to be a positive impact at all of the sites, with the most stable increase at Diablo Cove. Overall, the plant had the biggest impact species B. 


### 3. Fisheries and Invasive Species

```{r include=F}

fishery <- read_csv("fishery.csv") %>%
  na.omit()

adult_recruit <- read_csv("recruit_adult.csv")

recruit_adult <- read_csv("adult_recruit.csv")


```


```{r echo=F}


c_recruitCA_adult_OR <- ggplot(recruit_adult, aes(x = Recruit_Cancer_CA, y = Adult_Cancer_OR))+
  geom_point()+
  theme_bw()+
  labs(#title = "Adult Cancer Crab in Oregon with Recruitment in California",
       x = "California Cancer Recruitment",
       y = "Oregon Cancer Adults")

c_recruitCA_adult_OR



```


Cancer adults from Oregon affect the number of recruits in California because the current flows from north to south. When there are too many or too little adults, there is a small number of recruits. When there is median number of adults in Oregon, there is a high number of recruits in California. 













```{r echo=F}

barn_ca_upwelling <- ggplot(fishery, aes(x = Recruit_Barnacle_CA)) +
  geom_line(aes(y = Upwelling_Winter_CA, color = "Upwelling Winter")) +
  scale_color_manual(values = c("darkorange3", "cyan3"))+
  labs(title = "Recruitment of Barnacle Bill During Winter Upwelling in CA",
       x = "Barnacle Recruitment",
       y = "Winter Upwelling",
       color = "Season")+
  theme_bw()+
   theme(legend.position = "none")
  


barn_ca_upwelling


```



Recruitment of Barnacles in California depends heavily on Winter upwelling. As there is more upwelling during the winter in California, there is higher recruitment of Barnacles. 



