---
title: "Homework 4"
author: "Sidney Gerst"
date: "3/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

### 1. Climate Change 

```{r include = F}

climate_change <- read_csv("climate_change.csv")


```

**Development Mode**

```{r echo = F}

development_change <- ggplot(climate_change, aes(x = Species, y = density_change, fill = development)) +
  geom_bar(stat = "identity") +
  facet_wrap(~development, scales = "free_x") +
  labs(title = "Development Mode and the Change in Density from 1955",
       y = "Change in Density") +
  theme_bw()+
  theme(legend.position = "none") 

development_change


```

The chart above does not show a pattern of change in species density depending on if the species has a planktonic larval stage or not. Using the metric developmental model is not as helpful as the other metrics for assessing if climate change has an affect on species density. 



**Geographic Range**

```{r echo = F}

geographic <- ggplot(climate_change, aes(x = Species, y = density_change, fill = geographic_range))+
  geom_bar(stat = "identity")+
  facet_wrap(~geographic_range, scales = "free_x") +
  theme_bw()+
  labs(title = "Geographic Range and the Change in Density from 1955",
       y = "Change in Density") +
  theme(legend.position = "none")

geographic



```

There is a pattern for each of the different geographic ranges. The Cosmopolitan species are split between positive and negative density change. The Northern species all had a negative change in density from the year 1955. The Southern species all had a positive change in density from the year 1955. This shows that climate change has a positive effect on Southern species and a negative effect on Northern species. 


**Trophic Level**

```{r echo=F}

trophic <- ggplot(climate_change, aes(x = Species, y = density_change, fill = trophic_level))+
  geom_bar(stat = "identity")+
  facet_wrap(~trophic_level, scales = "free_x") +
  theme_bw()+
  labs(title = "Trophic Level and the Change in Density from 1955",
       y = "Change in Density") +
  theme(legend.position = "none")

trophic



```

Scavengers had the most positive effect from climate change where five out of six species showed a positive change in density. 


### 2. Nuclear Power

```{r include = F}

nuclear <- read_csv("nuclearpowerplant.csv")

nuclearspecies <- read_csv("nuclear_species.csv")


```


**Species A**

```{r echo=F}

speciesa <- ggplot(nuclearspecies, aes(x = Year, y = A, fill = Plant)) +
  geom_bar(stat = "identity") +
  facet_wrap(~Plant) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 38)) +
  labs(title = "Density of Species A",
       y = "Number of Individuals per 100m^2 ")
  

speciesa

```

 

**Species B**

```{r echo=F}

speciesb <- ggplot(nuclearspecies, aes(x = Year, y = B, fill = Plant)) +
  geom_bar(stat = "identity") +
  facet_wrap(~Plant) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 40)) +
  labs(title = "Density of Species B",
       y = "Number of Individuals per 100m^2 ")
  

speciesb


```



**Species C**

```{r echo=F}

speciesc <- ggplot(nuclearspecies, aes(x = Year, y = C, fill = Plant)) +
  geom_bar(stat = "identity") +
  facet_wrap(~Plant) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 40)) +
  labs(title = "Density of Species C",
       y = "Number of Individuals per 100m^2 ")
  

speciesc



```

Hyperion Bay should be used as the control because it tracks closely to Diablo before the plant became operational. There doesn't seem to be any detectable impacts on species A from any of the areas sampled. There were detecable impacts on species B with a distinct drop at Diablo and Hyperion and a steady decline with a few peaks at Noway Bay. For species C there seemed to be a positive impact at all of the sites, with the most stable increase at Diablo Cove. Overall, the plant had the biggest impact species B. 


### 3. Fisheries and Invasive Species

```{r include=F}

fishery <- read_csv("fishery.csv") %>%
  na.omit()

adult_recruit <- read_csv("recruit_adult.csv")


```

**Cancer Cancer**

```{r echo=F}
crabs <- adult_recruit %>%
  filter(Species == "Cancer") %>%
  na.omit()
  


crabplot <- ggplot(crabs, aes(x = Year)) +
  geom_line(aes(y = Adult, color = "Adult")) +
  geom_line(aes(y = Recruitment, color = "Recruitment"))+
  facet_wrap(~State)+
  scale_y_continuous(sec.axis = sec_axis(~., name = "Recruitment")) +
  theme_bw()+
  labs(title = "Cancer Densities of Adults and Recruitments",
       color = "Density") +
  scale_color_manual(values = c("blue", "red"))


crabplot

```


**Barnacles**

```{r echo=F}

barnacle <- adult_recruit %>%
  filter(Species == "Barnacle") %>%
  na.omit()
  


barnacleplot <- ggplot(barnacle, aes(x = Year)) +
  geom_line(aes(y = Adult, color = "Adult")) +
  geom_line(aes(y = Recruitment, color = "Recruitment"))+
  facet_wrap(~State)+
  scale_y_continuous(sec.axis = sec_axis(~., name = "Recruitment")) +
  theme_bw()+
  labs(title = "Barnacle Densities of Adults and Recruitments",
       color = "Density") +
  scale_color_manual(values = c("darkgreen", "purple"))


barnacleplot


```

**Cancer Recruitment and California Upwelling**

```{r echo=F}
recruit_upwelling <- ggplot(fishery, aes(x = Recruit_Cancer_CA)) +
  geom_line(aes(y = Upwelling_Winter_CA, color = "Upwelling Winter")) +
  geom_line(aes(y = Upwelling_Summer_CA, color = "Upwelling Summer")) +
  scale_y_continuous(sec.axis = sec_axis(~., name = "Summer")) +
  scale_color_manual(values = c("darkturquoise", "goldenrod1"))+
  labs(title = "Recruitment of Cancer Crabs During Upwelling in CA",
       x = "Cancer Recruitment",
       y = "Winter",
       color = "Season")+
  theme_bw()
  


recruit_upwelling


```



**Cancer Recruitment Oregon Upwelling**

```{r echo=F}

oregon_upwelling <- ggplot(fishery, aes(x = Recruit_Cancer_OR)) +
  geom_line(aes(y = Upwelling_Winter_OR, color = "Upwelling Winter")) +
  geom_line(aes(y = Upwelling_Summer_OR, color = "Upwelling Summer")) +
  scale_y_continuous(sec.axis = sec_axis(~., name = "Upwelling Summer")) +
  scale_color_manual(values = c("deeppink3", "lightseagreen"))+
  labs(title = "Recruitment of Cancer Crabs During Upwelling in OR",
       x = "Cancer Recruitment",
       y = "Winter",
       color = "Season")+
  theme_bw()
  


oregon_upwelling


```


**Barnacle Recruitment California Upwelling**

```{r echo=F}

barn_ca_upwelling <- ggplot(fishery, aes(x = Recruit_Barnacle_CA)) +
  geom_line(aes(y = Upwelling_Winter_CA, color = "Upwelling Winter")) +
  geom_line(aes(y = Upwelling_Summer_CA, color = "Upwelling Summer")) +
  scale_y_continuous(sec.axis = sec_axis(~., name = "Summer")) +
  scale_color_manual(values = c("darkorange3", "cyan3"))+
  labs(title = "Recruitment of Barnacle Bill During Upwelling in CA",
       x = "Barnacle Recruitment",
       y = "Winter",
       color = "Season")+
  theme_bw()
  


barn_ca_upwelling


```



**Barnacle Recruitment Oregon Upwelling**

```{r echo=F}

barn_or_upwelling <- ggplot(fishery, aes(x = Recruit_Barnacle_OR)) +
  geom_line(aes(y = Upwelling_Winter_OR, color = "Upwelling Winter")) +
  geom_line(aes(y = Upwelling_Summer_OR, color = "Upwelling Summer")) +
  scale_y_continuous(sec.axis = sec_axis(~., name = "Summer")) +
  scale_color_manual(values = c("slateblue1", "coral2"))+
  labs(title = "Recruitment of Barnacle Bill During Upwelling in OR",
       x = "Barnacle Recruitment",
       y = "Winter",
       color = "Season")+
  theme_bw()
  


barn_or_upwelling


```

