---
title: "Homework 1"
author: "Sidney Gerst"
date: "1/21/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load packages
library(tidyverse)
library(janitor)
library(
  ggpmisc)
library(lme4)

```


####1. Mean Density of Adults


```{r echo = F, message=F}

#read in adult data
all_org <- read_csv("adult_other.csv")

#filter for only the adult fish
adults_clean <- all_org %>%
  clean_names( case = "snake") %>%
  filter(grepl('Adult', organism)) %>%
  gather(place, Density, rarotonga_2009:aitutaki_2018)  %>%
  separate(place, c("Place", "Year"), "_") 

fish_plot <- ggplot(adults_clean, 
                       aes(fill = Year, x = Place, y = Density)) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  geom_errorbar(aes(ymin = Density, ymax = Density + ci), 
                width=.8, position=position_dodge(.9)) +
  facet_wrap(~organism, scales = "free_y") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
  labs(title = "Mean Number Adult Fish", y = "Density (number per 100 m^2 of reef)",
       x = "Lagoon")

fish_plot



```

For the Coral Trout and Spotted Damselfish, there is a significant decrease from 2009 to 2018 in both Aitutaki and Rarotonga. There is no significant difference in Surgeonfish from Aitutaki from 2009 to 2018, but there is in Rarotonga. The only instance where 2018 was significantly greater than 2009 in both Aitutaki and Rarotonga is with Yellow Dameslfish. 

####2. Young Fish Density


```{r echo = F, message=F, warning=F}

#read in young fish data
young_fish <- read_csv("young_fish.csv")

#convert year to numeric
young <- young_fish %>%
  select(organism:ci) %>%
  transform(year = as.character(year))

#plot it
young_plot <- ggplot(young, 
                       aes(fill = year, x = place, y = density_1m)) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  geom_errorbar(aes(ymin = density_1m, ymax = density_1m + ci), 
                width=.8, position=position_dodge(.9)) +
  facet_wrap(~organism, scales = "free_y") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_brewer("Year", palette="Set2") +
  labs(title = "Mean Number of Newly Recuited (young) Fish", 
       y = "Density (number per 1 m^2 of reef)",
       x = "Lagoon")

young_plot



```

Coral Trout recruits were the only young fish with a significant decrease from 2009 to 2018 in both Aitutaki and Rarotonga. The Spotted Damselfish did not show significant change in Aitutaki but did in Rarotonga. Surgeonfish did not show significant change in Aitutaki, but did in Rarotonga from 2009 to 2018. The Yellow Damselfish was the only fish to significantly increase from 2009 to 2018 in both Aitutaki and Rarotonga. 

####3. Microhabitat

```{r echo = F, message=F, warning=F}

#read in all organisms
young_fish <- read_csv("young_fish.csv")
adults_only <- read_csv("adults_only.csv")

#filter adtuls
adults_filtered<- adults_only %>%
  select(organism:ci) %>%
  na.omit() %>%
  rename(adult_density = density)

#calc young density
young_density <- young_fish %>%
  select(organism:microhabitat_100m) %>%
  filter() %>%
  transform(year = as.character(year))

<<<<<<< HEAD

young_density$recruit_density <- (young_density$density_1m*young_density$microhabitat_100m)
=======
young_density$recruit_density <- young_density$density_1m * young_density$microhabitat_100m
>>>>>>> acb28b4845275008fa09c017c99d0667fc35544e

#add adult density to young_density df
adult_young_merge <- cbind(young_density, adults_filtered[,4]) 

#find rsquared 
Rsqrd <- adult_young_merge %>% 
  group_by(organism ) %>% 
  summarize(R2 = summary(lm(recruit_density ~ adult_density))$r.squared)

Rsqrd <- mutate(Rsqrd, x = 16, y = 100, Label = paste("R^2=", round(R2, 4)))

#plot it
all_fish_plot <- ggplot(adult_young_merge, 
                       aes(
                           x = recruit_density, 
                           y = adult_density)) +
  geom_smooth(method=lm, se = F)+
  #geom_text(mapping = aes(x, y, label = Label), data = Rsqrd)+
  geom_point(size = 4, aes(
             color = place, 
              shape = factor(year))) +
  facet_wrap(~organism, scale = "free") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer("Place", palette="Set1") +
  labs(title = "Adult and Young Density per 100m^2 of Habitat",
       x = "Young Recruit",
       y = "Adult",
       color = "Place",
       shape = "Year")

all_fish_plot



```

The Spotted Damselfish is the second most correlated between young and adults of the four fish types (R^2= 0.94), and the Surgeonfish is the most (R^2= 0.9675). Coral Trout is also very correlated (R^2= 0.8958), and Yellow Dameselfish is least (R^2= 0.4017). 


#### 4. Adults and Microhabitat

```{r echo = F, message=F, error=F}

#regression of adults and microhabitat
adultr <- adult_young_merge %>% 
  group_by(organism ) %>% 
  summarize(R2 = summary(lm(adult_density ~ microhabitat_100m))$r.squared)

adultr <- mutate(adultr, x = 1.75, y = 50, Label = paste("R^2=", round(R2, 4)))

#plot
adult_micro_plot <- ggplot(adult_young_merge, 
                       aes(
                           x = microhabitat_100m, 
                           y = adult_density)) +
  geom_smooth(method=lm, se = F)+
  #geom_text(mapping = aes(x, y, label = Label), data = adultr)+
  geom_point(size = 4, aes(
             color = place , 
              shape = factor(year))) +
  facet_wrap(~organism, scale = "free") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
<<<<<<< HEAD
  scale_color_brewer("Place", palette="Set2") +
=======
  scale_color_brewer("Place", palette="Dark2") +
>>>>>>> acb28b4845275008fa09c017c99d0667fc35544e
  labs(title = "Adult and the Microhabitat used by their Young",
       x = "Microhabitat",
       y = "Adult",
       color = "Place",
       shape = "Year")

adult_micro_plot



```

The Yellow Dameslfish is the least correlated (R^2= 1e-04).
Coral Trout is second to least correlated (R^2= 0.7761).
Spotted Dameselfish and Surgeonfish are very correlated (R^2= 0.9482, R^2= 0.9646)

#### 5. Adults and Microhabitat Density

```{r message=F, echo=F, error=F, warning=F}

#find density of adults / microhabitat
adult_young_merge$adult_habitat <- adult_young_merge$adult_density/adult_young_merge$microhabitat_100m


#plot it
adult_habitat_plot <- ggplot(adult_young_merge, 
                       aes(fill = year, x = place, y = adult_habitat)) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  facet_wrap(~organism, scales = "free_y") +
  theme_classic() +
  scale_fill_brewer("Year", palette="Accent") +
  theme(plot.title = element_text(hjust = 0.5))+
  labs(title = "Adults per Microhabitat", y = "Adult Density (number per 100 m^2 of microhabitat)",
       x = "Lagoon")

adult_habitat_plot



```

Yellow Damselfish is the only fish that increased in both lagoons from 2009 to 2018 per Mounding Coral. Every other fish per their respective microhabitat (Coral Trout per Course-Branching Coral, Spotten Dameselfish per Sea Anenomoes, and Surgeonfish per Fine-branching Coral) decreased from 2009 to 2018. 

#### 6. Compare each fish 

```{r message=F, echo=F, error=F, warning=F}

#filter and plot by each fish pairs (6 total plots)

surgeon <- adult_young_merge %>%
  filter(organism == "Surgeonfish") %>%
  rename(surgeon_density = adult_density)

coral_trout <- adult_young_merge %>%
  filter(organism == "Coral Trout") %>%
  rename(coral_density = adult_density)

yellow <- adult_young_merge %>%
  filter(organism == "Yellow Damselfish") %>%
  rename(yellow_density = adult_density)

spotted <- adult_young_merge %>%
  filter(organism == "Spotted Damselfish") %>%
  rename(spotted_density = adult_density)

#merge surgeon and coral
surgeon_coral <- cbind(surgeon, coral_trout[,9, drop=FALSE])

#find r2
sc_r <- surgeon_coral %>%
summarize(R2 = summary(lm(surgeon_density ~ coral_density))$r.squared)

sc_r <- mutate(sc_r, x = 150, y = 150, Label = paste("R^2=", round(R2, 4)))

#plot
surgeon_coral_plot <- ggplot(surgeon_coral, aes(x = surgeon_density, y = coral_trout[,9])) +
  geom_smooth(method = lm, se=F) +
  geom_text(mapping = aes(x, y, label = Label), data = sc_r)+
  geom_point(size = 4, aes(
             color = place, 
              shape = factor(year)))+
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer("Place", palette="Set1") +
  labs(title = "Surgeonfish and Coral Trout",
       x = "Surgeonfish Density",
       y = "Coral Trout Density",
       color = "Place",
       shape = "Year")

surgeon_coral_plot

#merge surgeon and spotted
surgeon_spotted <- cbind(surgeon, spotted[,9, drop=FALSE])

#find r2
ss_r <- surgeon_spotted %>%
summarize(R2 = summary(lm(surgeon_density ~ spotted_density))$r.squared)

ss_r <- mutate(sc_r, x = 150, y = 750, Label = paste("R^2=", round(R2, 4)))

#plot
surgeon_spotted_plot <- ggplot(surgeon_spotted, aes(x = surgeon_density, y = spotted_density)) +
  geom_smooth(method = lm, se=F) +
  geom_text(mapping = aes(x, y, label = Label), data = ss_r)+
  geom_point(size = 4, aes(color = place, 
                          shape = factor(year)))+
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer("Place", palette="Set1") +
  labs(title = "Surgeonfish and Spotted Dameselfish",
       x = "Surgeonfish Density",
       y = "Spotted Dameselfish Density",
       color = "Place",
       shape = "Year")

surgeon_spotted_plot

#merge surgeon and yellow
surgeon_yellow <- cbind(surgeon, yellow[,9, drop=FALSE])

#find r2
sy_r <- surgeon_yellow %>%
summarize(R2 = summary(lm(surgeon_density ~ yellow_density))$r.squared)

sy_r <- mutate(sc_r, x = 150, y = 90, Label = paste("R^2=", round(R2, 4)))

#plot
surgeon_yellow_plot <- ggplot(surgeon_yellow, aes(x = surgeon_density, y = yellow_density)) +
  geom_smooth(method = lm, se=F) +
  geom_text(mapping = aes(x, y, label = Label), data = sy_r)+
  geom_point(size = 4, aes(color = place, 
                          shape = factor(year)))+
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer("Place", palette="Set1") +
  labs(title = "Surgeonfish and Yellow Damselfish",
       x = "Surgeonfish Density",
       y = "Yellow Damselfish Density",
       color = "Place",
       shape = "Year")

surgeon_yellow_plot


#merge coral and spotted
coral_spotted <- cbind(coral_trout, spotted[,9, drop=FALSE])

#find r2
cs_r <- coral_spotted %>%
summarize(R2 = summary(lm(coral_density ~ spotted_density))$r.squared)

cs_r <- mutate(sc_r, x = 50, y = 750, Label = paste("R^2=", round(R2, 4)))

#plot
coral_spotted_plot <- ggplot(coral_spotted, aes(x = coral_density, y = spotted_density)) +
  geom_smooth(method = lm, se=F) +
  geom_text(mapping = aes(x, y, label = Label), data = cs_r)+
  geom_point(size = 4, aes(color = place, 
                          shape = factor(year)))+
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer("Place", palette="Set1") +
  labs(title = "Coral Trout and Spotted Damselfish",
       x = "Coral Trout Density",
       y = "Spotted Damselfish Density",
       color = "Place",
       shape = "Year")

coral_spotted_plot


#merge coral and yellow
coral_yellow <- cbind(coral_trout, yellow[,9, drop=FALSE])

#find r2
cy_r <- coral_yellow %>%
summarize(R2 = summary(lm(coral_density ~ yellow_density))$r.squared)

cy_r <- mutate(sc_r, x = 50, y = 90, Label = paste("R^2=", round(summary(lm1)$r.squared,4)))

#plot
coral_yellow_plot <- ggplot(coral_yellow, aes(x = coral_density, y = yellow_density)) +
  geom_smooth(method = lm, se=F) +
  geom_text(mapping = aes(x, y, label = Label), data = cy_r)+
  geom_point(size = 4, aes(color = place, 
                          shape = factor(year)))+
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer("Place", palette="Set1") +
  labs(title = "Coral Trout and Yellow Damselfish",
       x = "Coral Trout Density",
       y = "Yellow Damselfish Density",
       color = "Place",
       shape = "Year")

coral_yellow_plot

#merge spotted and yellow
spotted_yellow <- cbind(spotted, yellow[,9, drop=FALSE])

#find r2
sy_r <- spotted_yellow %>%
summarize(R2 = summary(lm(spotted_density ~ yellow_density))$r.squared)

sy_r <- mutate(sc_r, x = 750, y = 90, Label = paste("R^2=", round(R2, 4)))

#plot
spotted_yellow_plot <- ggplot(spotted_yellow, aes(x = spotted_density, y = yellow_density)) +
  geom_smooth(method = lm, se=F) +
  geom_text(mapping = aes(x, y, label = Label), data = sy_r)+
  geom_point(size = 4, aes(color = place, 
                          shape = factor(year)))+
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_color_brewer("Place", palette="Set1") +
  labs(title = "Spotted Damselfish and Yellow Damselfish",
       x = "Spotted Damselfish Density",
       y = "Yellow Damselfish Density",
       color = "Place",
       shape = "Year")

spotted_yellow_plot


```

As Surgeonfish decrease in Rarotonga, Coral Trout decrease. As Surgeonfish increase in Aitutaki, Coral Trout decrease. The overal trend is postive, but isn't very strongly correlated.  

As Surgeonfish decrease in Rarotonga, Spotted Damselfish decrease. As Surgeonfish increase in Aitutaki, Spotted Damselfish decrease. The overal trend is postive, but isn't very strongly correlated. 

As Surgeonfish increased in Rarotonga, Yellow Damselfish decreased. As Surgeonfish increased, Yellow Damselfish increased in Aitutaki. Overall the trend is negative, but it isn't strongly correlated. 

As Coral Trout decreased, Spotted Damselfish decreased in both Rarotonga and Aitutaki from 2009 to 2018. 

From 2009 to 2018, Coral Trout decreased as Yellow Damselfish increased in Rarotonga and Aitutaki. 

<<<<<<< HEAD
#### 5. Adults and Lagoons

```{r}

#clean adult young habitat df
adult_young_habitat <- adult_young_merge %>%
  rename(adult_density = density) %>%
  transform(year = as.character(year))



#find density of adults per habitat
adult_young_habitat$adult_habitat_density <- adult_young_habitat$adult_density / adult_young_habitat$microhabitat_100m

#plot it
adult_habitat_plot <- ggplot(adult_young_habitat, 
                       aes(fill = year, x = place, y = adult_habitat_density)) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  facet_wrap(~organism, scales = "free_y") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))+
  scale_fill_brewer("Year", palette="Set3") +
  labs(title = "Density of Adults per Microhabitat used by their Recruits", 
       y = "Density (number per 100 m^2 of reef)",
       x = "Lagoon")

adult_habitat_plot




```


Talk about the trends

#### 6. Fish Comparisons

```{r}




```

=======
In both Rarotonga and Aitutaki, as Spotted Damselfish decreased, Yellow Damselfish increased from 2009 to 2018. 
>>>>>>> acb28b4845275008fa09c017c99d0667fc35544e
