---
title: "Homework 2"
author: "Sidney Gerst"
date: "February 9, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

###1. Alternative Hypothesis for non-fish 

```{r echo = F, message=F, warning=F}
all_organisms <- read_csv("all_organsims.csv")

nonfish <- all_organisms %>%
  filter(grepl('Other', organism)) %>%
  select(-microhabitat) %>%
  transform(year = as.character(year))

other_plot <- ggplot(nonfish, 
                       aes(fill = year, x = place, y = density)) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  geom_errorbar(aes(ymin = density, ymax = density + ci), 
                width=.8, position=position_dodge(.9)) +
  facet_wrap(~organism, scales = "free_y") +
  theme_classic() +
  scale_fill_brewer("Year") +
  theme(plot.title = element_text(hjust = 0.5))+
  labs(title = "Mean Number Non-fish", y = "Density (number per 100 m^2 of reef)",
       x = "Lagoon")

other_plot



```


####Aglae

(H1): Algae might have increased in both lagoons because coral might decrease due to agriculture production or increased climatic events such as cyclones coming into the area. 
(H2): Algae might increase in one of the lagoons because coral will still be abundant in Aitutaki, especially Fine-Branching and Mounding corals. 

####Coarse-Branching Corals

(H1): Coarse-Branching Corals might decrease due to the presence of algae. Algae tends to be a big competitor when space previously used by Coarse-Branching corals is open. Once algae is stable, it is hard for corals to make a come back. 
(H2): Coarse-Branching Corals might decrease due to a decrease in young Coral Trout recruitment. Recruitment of young fish is vital to the growth of corals. They excrete ammonia that the corals use as a fertilizer. 

####Fine-Branching Corals

(H1): Fine-Branching Coral might decrease due to an increase in algae in Rarotogna
(H2): A steady population of Surgeon recruitment might increase the amount of Fine-Branching Corals in Aitutaki

####Mounding Coral

(H1): An unsignificant change in Yellow Damselfish might change a similar unsignificant change in Mounding Coral

(H2): Mounding coral might not be effected by algae, and remain constant in both lagoons. 

####Sea Anemones

(H1): Sea Anemones might have decreased significantly due to poor Spotted Dameselfish recruitment in Rarotonga and increased algae in Rarotonga

(H2): Sea Anemones might have decreased significantly in Aitutaki due from Fine-Branching corals and Mounding corals increasing and out competing them. 

###Alternative Hypotheses for Spotted Damselfish and Yellow Damselfish

```{r echo = F, message=F, warning=F}

damselfish <- all_organisms %>%
  filter(grepl( 'Damselfish', organism)) %>%
  filter(grepl( 'Adult', organism)) %>%
  select(-microhabitat) %>%
  transform(year = as.character(year))

damselfish_plot <- ggplot(damselfish, 
                       aes(fill = year, x = place, y = density)) +
  geom_bar(position = "dodge", stat = "identity", color = "black") +
  geom_errorbar(aes(ymin = density, ymax = density + ci), 
                width=.8, position=position_dodge(.9)) +
  facet_wrap(~organism, scales = "free_y") +
  theme_classic() +
  scale_fill_brewer("Year", palette="Set2") +
  theme(plot.title = element_text(hjust = 0.5))+
  labs(title = "Mean Number Damselfish", y = "Density (number per 100 m^2 of reef)",
       x = "Lagoon")

damselfish_plot


```

####Spotted Damselfish

(H1): Adult Spotted Damselfish may have significantly decreased due to significantly decreasing Sea Anenomes (their preferred microhabitat during young recruitment). 

(H2): Adult Spotted Damselfish maybe have significantlly decreased due to the significantly increasing Yellow Damselfish. Even though their young recruit on different microhabitats, their adult stages may compete for similar resources. 

####Yellow Damselfish

(H1): 